### 2015-03-27 tex/related.tex
removing duplicate
Brought in abstract, intro, and related work from CAV paper.

In this section we discuss some closely related works, including
techniques for scaling symbolic execution of programs with complex
data types and heap summary techniques. Note that there is a huge body
of work on analyzing programs with heaps in the domain of static
analysis, testing, and verification.

Initial work on symbolic execution largely focused on checking
properties of imperative programs with primitive primitive
types~\cite{Clarke:76,King:76}. Several recent projects generalized
the core idea of symbolic execution which enabled it to be applied to
programs with more general types, including references and
arrays~\cite{GSE03,Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit}.
Our work leverages the core idea in generalized symbolic execution
with lazy initialization to construct the heap on-the-fly during
symbolic execution, but avoids the nondeterminism introduced by GSE by
constructing a summary heap and will generally create fewer paths than
GSE techniques.

Pex is a tool for dynamic symbolic execution for .NET programs. In
order to handle data structures Pex uses a theory of arrays and does
not initialization~\cite{export:81193}.  It is required to have a
constraint solver that handles the theory for unbounded arrays for
this approach to be tractable. It would be an interesting comparision
to perform in future work.

A number of static analysis techniques have been proposed to support
reasoning about input heap structures. The technique most closely
related to (and which served as inspiration for) our approach is the
procedure summary proposed by Dillig et al. to support modular
reasoning~\cite{Dillig:2011}.  While their method improves path
sensitivity over standard static analysis methods, it remains limited
by a statically-generated symbolic input heap and it cannot adapt to
path-sensitive heap properties of the input heap.

Other techniques have been proposed to model references using sets of
guarded
locations~\cite{Xie:2005,Cherem:2007,Dillig:2011,Sen:2014}. These
sets, sometimes known as value sets or value summaries, allow multiple
heaps to be represented simultaneously with a higher degree of
precision than afforded by shape analysis. However, some of these
previous attempts~\cite{Xie:2005,Cherem:2007} utilize non-local
recursive definitions for objects.  In our heap representation, object descriptions are
entirely local, thus avoiding these pitfalls. Other methods
\cite{Dillig:2011,Sen:2014}, while having local morphological
representations, do not provide for dynamic exploration of the initial
heap state.

There is also a large body of work on generating tests for
object-oriented programs that use a variety of techniques to generate
heap structures to test object-oriented
programs~\cite{xie2005symstra,xie2004rostra,boyapati2002korat,artzi2006finding}.
Another line of work in heap representation lies in identifying
isomorphic heap structures in order to avoid exploring redundant
paths~\cite{milicevic2007korat}.  These methods are generally focused
on the morphology of the heap apart from the external constraint
problems encountered during program execution, and as such, are
largely orthogonal to this work. Recent work shows that the need for
reasoning about heap structures is an important
problem~\cite{barr2013collecting}. Delta execution is another work
that combines states for object-oriented programs~\cite{d2008delta}.

%The impact of such an approach is two-fold.  First, these techniques
%must use approximations to resolve reference inequalities, resulting
%in false positives in the results. Second, these techniques are
%incapable of reasoning about heaps with recursive data structures due
%to the potential for infinite recursion during dereferencing. This
%means that either a large class of data structures must be avoided,
%or a large class of behaviors must be ignored.

>>>>

Initial work on symbolic execution largely focused on checking
properties of imperative programs with primitive
types~\cite{Clarke:76,King:76}.
Several projects have generalized the core idea of symbolic execution,
enabling it to be applied to programs with more general types,
including references and
arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these
generalized symbolic execution (\gsetxt{}) techniques work by branching over
multiple copies of the system state during dereferencing operations,
exacerbating path explosion.
Our work leverages the core idea in generalized symbolic execution
with lazy initialization using on-the-fly reasoning to model a
black-box input heap during symbolic execution, but avoids the
nondeterminism introduced by~\gsetxt{} by constructing a single
symbolic heap and polynomially-sized path condition for each control
flow path.

Recent progress has been made towards mitigating path explosion via state merging~\cite{Kuznetsov:2012,Sen:2014,Torlak:2014}. While the independently developed techniques in~\cite{Sen:2014,Torlak:2014} use representations similar to the one presented here, none of these techniques address the fundamental issue concerning symbolic heaps, namely dereferencing symbolic input references. For these reasons, we believe these works to be both orthogonal and complimentary to our own.

A number of dynamic symbolic execution (\dsetxt{}) techniques either use
concretization when reasoning about references or require solvers that
support theories of
arrays~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}. Sometimes,
however, as demonstrated in~\cite{Elkarablieh:2009},~\dsetxt{}
under-approximates the possible heaps configurations when it
concretizes symbolic values. The SAGE~\dsetxt{}
engine~\cite{Elkarablieh:2009} includes more sophisticated methods for
reasoning about references, and can successfully reason about more
complicated examples. However, the heap model in SAGE prohibits
input-dependent memory allocation. The fixed-memory requirement means
that analyses of programs accepting indefinite input heaps may
terminate prematurely, even for the class of self-limiting
solver-compatible programs.

Many bounded model checking (BMC) methods include a model for
reasoning about references, including those described
in~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}. However,
BMC techniques generally need to predetermine bounds of a heap. Other
limitations include assuming that symbolic references do not
alias~\cite{Xie:2005,Babic:2007}, that data structures are not
recursive~\cite{Dillig:2011}, or prohibiting dereferencing of
black-box input references~\cite{Clarke:2004}.

A number of constraint-based programming techniques are capable of
reasoning about
heaps~\cite{Degrave:2010,Charreteur:2009,Albert:2013}. Most notably,
the technique in~\cite{Albert:2013} is capable of reasoning about
dereferencing operations in a per-path set of unknown input
heaps. However, no guarantees are made about the precision of the
analysis performed.

The symbolic heap value sets presented in this work build upon a
number of prior techniques that use sets of guarded values to
represent program
state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}. The
methods presented in~\cite{Sen:2014,Torlak:2014,Yorsh:2008} use value
sets to represent all symbolic program state, including
references. While symbolic referencing operations could, in principle,
be supported with these methods, it is not clear from the published
material exactly how that might be accomplished, especially when
reasoning about dereferencing in a black-box input heap. All of the
methods presenting solutions to the dereferencing
problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} are not complete,
for a variety of reasons which have been previously enumerated.
